### 2004-07-19 Documentation/Manual.tex
Editing done ;-)

\input{tumlogo}

\begin{minipage}{7cm}
\begin{center}
{\bf Technische Universit{\"a}t M{\"u}nchen} \\
Physik-Department \\
Institut f{\"u}r Theoretische Physik, T30d \\
\end{center}
\end{minipage}

\vspace{-2cm}

\hfill \oTUM{3.5cm}

\vspace{3cm}

\begin{center}
{ \Large \bf
\GLOBES\ 1.X \\
General Long Baseline Experiment Simulator \\ }
\vspace*{0.5cm}
{\large \bf User's and experiment definition manual }

@@

\GLOBES\ is mainly developed for academic use. Thus The \GLOBES\ Team would
appreciate being given academic credit for it. Whenever you use \GLOBES\
to produce a publication or a talk indicate that you have used \GLOBES\ and
please cite the following reference
\begin{quote}
P. Huber, M. Lindner and W. Winter ... 
\end{quote}
and \emph{not} this manual. This manual does not constitute a scientific 
publication and will not be submitted to any scientific journal. 
It will evolve during time since it is intendend for 
regular revision.
Besides, many of the data which is used by \GLOBES\ and distributed together
with it should be correctly referenced where possible. For details see the
???.

@@

\bibliographystyle{./unsrt}
\bibliography{references}

>>>>

\vspace*{3cm}

\begin{center}
{ \Large \bf
\GLOBES\ 2.0 \\
General Long Baseline Experiment Simulator \\ }
\vspace*{0.5cm}
{\large \bf User's and experiment definition manual }

@@

\GLOBES\ is mainly developed for academic use. Thus The \GLOBES\ Team would
appreciate being given academic credit for it. Whenever you use \GLOBES\
to produce a publication or a talk indicate that you have used \GLOBES\ and
please cite the following reference~\cite{globes_paper}
\begin{quote}
P. Huber, M. Lindner and W. Winter ... 
\end{quote}
and \emph{not} this manual. This manual does not constitute a scientific 
publication and will not be submitted to any scientific journal. 
It will evolve during time since it is intendend for 
regular revision.
Besides, many of the data which is used by \GLOBES\ and distributed together
with it should be correctly referenced where possible. For details see the
corresponding sub-section of the bibliography.

@@

\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{./unsrt}
\bibliography{references}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Referencing the data in \GLOBES}
\label{ref_data}

\index{norm}{Referencing!data in \GLOBES}
\GLOBES\ wouldn't be of much use without having high quality input data.
Much of this input data has been published somewhere and the authors
of those publication would appreciate to be cited by the user
when he/she is using their work. It is solely the user's responsibility 
to make sure that he/she understand where a certain input for \GLOBES\ comes
from and wether additional work has to be cited in addition to the 
\GLOBES\ paper~\cite{globes_paper}. To help this task we provide here the
necessary information for the data which is shiped together with \GLOBES.

When using the built-in earth matter profile, the original source is 
reference~\cite{Stacey}.

All files ending with \verb+.dat+ or \verb+.glb+ 
in the \verb+data+ subdirectory of the \GLOBES\ tar-ball have at their
beginning a comment field which clearly indicates which works should be
cited when using a certain file. Make sure that dependencies are correctly
tracked, \ie\ in some cases files included by other files have to checked
also. One can use the \verb+-v3+ option to \verb+globes+ to see which files
are included.

It is advisable to use the same style for your own input files, since in
case they are distributed, everbody will know how to correctly reference your
work.

### 2004-07-19 Documentation/appendix.tex
part 1 finis
Editing done ;-)

All those libraries are also available as rpm's from the various
distributors of GNU/Linux: See their web sites for downloads. Due to
the rather difficult nature of the build process of BLAS and LAPACK,
it is recommended that one use a suitable rpm instead. In addition,
there is a good chance that
gcc, f2c and GSL are already part of your installation. Furthmore, you need
a working \verb+make+ to build and install \GLOBES.

@@

The install target also will install a program with name \verb+globes+ to
\verb+$prefix+.

@@

In general it is advisable to use the shared libraries. If you don't
have root privileges, see the corresponding section of this file.
If you install \GLOBES\ with root privileges, do not forget to run 
{\tt ldconfig} after installation.

@@

\item Since you've installed a library don't forget to run \verb+ldconfig+ !
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Installation without root privilege}
\index{norm}{Installation!w/o root privilege}

@@

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

>>>>

All those libraries are also available as rpm's from the various
distributors of GNU/Linux: See their web sites for downloads. Due to
the rather difficult nature of the build process of BLAS and LAPACK,
it is recommended that one uses a suitable rpm instead. In addition,
there is a good chance that
gcc, f2c and GSL are already part of your installation. Furthmore, you need
a working \verb+make+ to build and install \GLOBES.

@@

The install target also will install a program with name \verb+globes+ to
\verb+$prefix/bin+.

@@

In general it is advisable to use the shared libraries. If you don't
have root privileges, see the corresponding section 
(page~\pageref{inst_noroot}).
If you install \GLOBES\ with root privileges, do not forget to run 
{\tt ldconfig} after installation.

@@

\item Since you've installed a library don't forget to run \verb+ldconfig+ !
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Installation without root privilege}
\index{norm}{Installation!w/o root privilege}
\label{inst_noroot}

@@
